---
title: "mnthemes"
format: gfm
execute: 
  echo: true
  warning: false
  message: false
editor: source
---

[![Experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)


```{r}
#| label: setup
#| include: false

#library(mnthemes)
library(ggplot2)
library(ggtext)
library(cowplot)
library(magick)
source("R/base_theme.R")
source("R/base_theme_dark.R")
source("R/theme_mn.R")
source("R/theme_mn_dark.R")
source("R/title_banner.R")
source("R/add_mn_logo.R")
source("R/mn_color_2_hex.R")
```


Minnesota state brand themes and helper functions for ggplot2. Includes default styles and state agency logos.


---

## Installation

You can install the development version from GitHub:

```{r, eval = FALSE}
# install.packages("remotes")
remotes::install_github("tidy-MN/mnthemes")
```

---

## Examples

### `theme_mn()`
```{r}
p <- ggplot(mtcars, aes(x = mpg, y = wt), ) + 
      labs(title = "Minnesota branded plot",
           subtitle = "Ope! Things are going downhill but not too bad. Overall could be worse.",
           caption = "Data from somewhere, 2024-2025",
           x = "MPG",
           y = "Weight") +
      lims(x = c(10, NA), y = c(0, NA)) 

p + 
  geom_point(color = "#003865", size = 7, alpha = 0.5) +
  theme_mn()
```

### `theme_mn_dark()`
```{r}
p + 
  geom_point(color = mn_color("gold"), size = 12, alpha = 0.75) + #"#F0F0F0"
  theme_mn_dark()
```


### `theme_mn_dark()` - Gold
```{r}
p + 
  geom_point(color = "white", size = 12, alpha = 0.75) + #"#F0F0F0"
  theme_mn_dark(text_color = mn_color("gold"))
```


### `theme_mn_dark()` - Green
```{r}
p + 
  geom_point(color = "white", fill = scales::alpha(mn_color("gold"), 0.75),
             size = 15, shape = 21) + 
  geom_smooth(color = mn_color("offwhite")) +
  theme_mn_dark(bg_color = "accent green", text_color = "white")
```


### `theme_mn_dark()` - Green | White banner
```{r}
p + 
  geom_point(color = "white", fill = scales::alpha(mn_color("gold"), 0.75),
             size = 15, shape = 21) + 
  geom_smooth(color = mn_color("offwhite")) +
  theme_mn_dark(bg_color = "accent green", 
                text_color = "white",
                banner = TRUE,
                banner_color = "offwhite",
                banner_text_color = "accent green")
```


### `theme_mn_dark()` - Green | Gold banner
```{r}
p + 
  geom_point(color = "white", fill = scales::alpha(mn_color("gold"), 0.75),
             size = 12, shape = 21) + 
  #geom_smooth(color = mn_color("offwhite")) +
  theme_mn_dark(bg_color = "accent green", 
                text_color = "white",
                banner = TRUE,
                banner_color = "gold",
                banner_text_color = "accent_green",
                banner_alpha = 0.85)
```

### With logo
```{r}
p <- p + 
     geom_point(color = "#003865", size = 7, alpha = 0.5) +
     theme_mn() 

p |> add_mn_logo()
p |> add_mn_logo("mdh", logo_width = 0.18)
p |> add_mn_logo("mpca", logo_width = 0.28)

## Dark mode logos
p <- p + geom_point(color = mn_color("gold"), size = 7, alpha = 0.7) + theme_mn_dark(bg_color = "accent green", text_color = "white")
p |> add_mn_logo("mpca-inverse", logo_width = 0.24, bg_color = "accent green")
```


---

## Features

- **Themes**: Minnesota branded themes (`theme_mn()`, `theme_mn_dark()`, …)  
- **Logos**: Add agency logo to plot (`add_mn_logo()`, `add_mn_logo("MPCA")`)  

---

## Contributing

Contributions are welcome! If you’d like to suggest styles or improvements, open an issue or pull request on GitHub.

---

## License

This package is released under the MIT License.

---

## Acknowledgements

Built on the shoulders of [ggplot2](https://ggplot2.tidyverse.org/) and [hrbrthemes](https://github.com/hrbrmstr/hrbrthemes).  

---

```bash
quarto render README.qmd --to gfm
```